---
title: "RMST & Stats Tests"
author: "Zihan Nie"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
  pdf_document:
    toc: yes
subtitle: "DAR Project group: 'DeFi'"
---
```{r setup, include=FALSE}
# Required R package installation; RUN THIS BLOCK BEFORE ATTEMPTING TO KNIT THIS NOTEBOOK!!!
# This section  install packages if they are not already installed. 
# This block will not be shown in the knit file.
knitr::opts_chunk$set(echo = TRUE)

# Set the default CRAN repository
local({r <- getOption("repos")
       r["CRAN"] <- "http://cran.r-project.org" 
       options(repos=r)
})

# Required packages for M20 LIBS analysis
if (!require("rmarkdown")) {
  install.packages("rmarkdown")
  library(rmarkdown)
}
if (!require("tidyverse")) {
  install.packages("tidyverse")
  library(tidyverse)
}
if (!require("stringr")) {
  install.packages("stringr")
  library(stringr)
}

if (!require("ggbiplot")) {
  install.packages("ggbiplot")
  library(ggbiplot)
}

if (!require("pheatmap")) {
  install.packages("pheatmap")
  library(pheatmap)
}
if(!require("randomForest")) {
  install.packages("randomForest")
  library(randomForest)
}
if(!require("caret")) {
  install.packages("caret")
  library(caret)
}
if(!require("survival")){
  install.packages("survival")
  library(survival)
}
if(!require("survminer")){
  install.packages("survminer")
  library(survminer)
}
if(!require("ggplot2")){
  install.packages("ggplot2")
  library(ggplot2)
}

if(!require("kableExtra")){
  install.packages("kableExtra")
  library(kableExtra)
}
if(!require("rpart")){
  install.packages("rpart")
  library(rpart)
}

if(!require("survRM2")){
  install.packages("survRM2")
  library(survRM2)
}

library(dplyr)
library(survival)
library(splines)
library(gridExtra)  # For arranging multiple plots
library(tibble)  # For creating summary tables
library(survRM2)
```
### Sample code of RMST Calculation
Below, we calculate the RMST values for each pair of the index and outcome event using three levels of tau as the convergence tolerance thresholds (1%, 5%, and 10%). 
* Caution: May take a while to run the following code. 
```{r}
# Define index events and corresponding outcome events
index_events <- list(
  "Borrow" = c("Account Liquidated", "Deposit", "Full Repay", "Liquidation Performed", "Repay", "Withdraw"),
  "Deposit" = c("Account Liquidated", "Borrow", "Liquidation Performed", "Repay", "Withdraw"),
  "Repay" = c("Account Liquidated", "Borrow", "Deposit", "Liquidation Performed", "Withdraw"),
  "Withdraw" = c("Account Liquidated", "Borrow", "Deposit", "Liquidation Performed", "Repay")
)

# List to store plots and convergence data
km_plots <- list()
rmst_plots <- list()
convergence_results <- tibble(IndexEvent = character(), OutcomeEvent = character(), ConvergedTau_1 = numeric(), ConvergedRMST_1 = numeric(), ConvergedTau_5 = numeric(), ConvergedRMST_5 = numeric(), ConvergedTau_10 = numeric(), ConvergedRMST_10 = numeric())
plot_index <- 1

# Loop through each index event and outcome event pair to create survival data
for (indexEvent in names(index_events)) {
  for (outcomeEvent in index_events[[indexEvent]]) {
    # Create the file path
    survivalData_path <- paste0("/academics/MATP-4910-F24/DAR-DeFi-LTM-F24/Data/Survival_Data/",
                                indexEvent, "/", outcomeEvent, "/survivalData.rds")
    
    # Read the survival data
    survivalData <- tryCatch({
      read_rds(survivalData_path)
    }, error = function(e) {
      warning(paste("Could not read file:", survivalData_path))
      next  # Skip to the next iteration if file not found
    })
    
    # Clean the data
    survivalData_clean <- survivalData %>%
      filter(!is.na(timeDiff) & timeDiff > 0 & !is.na(status))
    
    # Check if the cleaned data is empty or malfunctioning
    if (nrow(survivalData_clean) == 0) {
      warning(paste("Data is empty or malfunctioning for pair:", indexEvent, "to", outcomeEvent))
      next  # Skip to the next iteration if data is empty
    }
    
    # Ensure timeDiff is numeric and convert to days
    survivalData_clean$timeDiff <- as.numeric(survivalData_clean$timeDiff) / 86400  # Convert seconds to days
    
    # Create the survival object
    surv_object <- Surv(time = survivalData_clean$timeDiff, event = survivalData_clean$status)
    
    # Fit the Kaplan-Meier estimator
    km_fit <- survfit(surv_object ~ 1)
    
    # Extract times and survival probabilities from the Kaplan-Meier fit
    times <- km_fit$time
    surv_probs <- km_fit$surv
    
    # Ensure the start at time = 0
    times <- c(0, times)
    surv_probs <- c(1, surv_probs)
    
    # Fit a monotonic spline to the survival probabilities
    spline_fit <- splinefun(times, surv_probs, method = "monoH.FC")  # Monotonic spline to reduce extreme gradients
    
    # Define a sequence of cutoff times to evaluate RMST convergence
    tau_values <- seq(1, min(600, max(times)), by = 1)  # Evaluate RMST from day 1 to up to 600 or max observed days
    rmst_values <- numeric(length(tau_values))
    
    # Calculate RMST for each cutoff value with a try-catch to handle potential integration errors
    for (i in seq_along(tau_values)) {
      tau <- tau_values[i]
      
      # Use tryCatch to handle integration issues gracefully
      rmst_values[i] <- tryCatch({
        integrate(spline_fit, lower = 0, upper = tau)$value
      }, error = function(e) {
        # If there's an error, return NA and print a warning
        NA
      })
    }
    
    # Remove NA values for plotting
    valid_indices <- !is.na(rmst_values)
    valid_tau_values <- tau_values[valid_indices]
    valid_rmst_values <- rmst_values[valid_indices]
    
    # Find the point where RMST converges (change is below a tolerance level for 1%, 5%, or 10%)
    convergence_thresholds <- c(0.01, 0.05, 0.10)  # 1%, 5%, 10% thresholds
    converged_values <- list(NA, NA, NA, NA, NA, NA)
    for (tolerance in convergence_thresholds) {
      converged_index <- which(abs(diff(valid_rmst_values) / valid_rmst_values[-length(valid_rmst_values)]) < tolerance)[1]  # Find the first instance where relative change is below tolerance
      
      if (!is.na(converged_index)) {
        converged_tau <- valid_tau_values[converged_index + 1]
        converged_rmst <- valid_rmst_values[converged_index + 1]
        if (tolerance == 0.01) {
          converged_values[1] <- round(converged_tau, 2)
          converged_values[2] <- round(converged_rmst, 2)
        } else if (tolerance == 0.05) {
          converged_values[3] <- round(converged_tau, 2)
          converged_values[4] <- round(converged_rmst, 2)
        } else if (tolerance == 0.10) {
          converged_values[5] <- round(converged_tau, 2)
          converged_values[6] <- round(converged_rmst, 2)
        }
      }
    }
    
    convergence_results <- convergence_results %>%
      add_row(IndexEvent = indexEvent, OutcomeEvent = outcomeEvent, ConvergedTau_1 = converged_values[[1]], ConvergedRMST_1 = converged_values[[2]],
              ConvergedTau_5 = converged_values[[3]], ConvergedRMST_5 = converged_values[[4]],
              ConvergedTau_10 = converged_values[[5]], ConvergedRMST_10 = converged_values[[6]])
    
    plot_index <- plot_index + 1
  }
}

# Print the entire table with all rows and columns
print(convergence_results, n = nrow(convergence_results))

# Title for the table
cat("\nSummary of RMST Convergence Points Across Index and Outcome Event Pairs\n")

```


### Sample code for applying the Friedman test to all model's accuracy results and apply the Dunn's Test for post hoc pairwise comparison. 
```{r}
# Sample accuracy data as a matrix: Each row is a dataset, and each column is a model
accuracy_data <- data.frame(
  Logistic_Regression = c(0.85, 0.78, 0.80, 0.82, 0.87),
  AdaBoost = c(0.88, 0.81, 0.84, 0.83, 0.86),
  SVM_Linear = c(0.86, 0.80, 0.82, 0.81, 0.85),
  Naive_Bayes = c(0.82, 0.77, 0.78, 0.80, 0.79),
  GBM = c(0.89, 0.83, 0.85, 0.84, 0.88)
)

# Transpose the data to ensure it has the correct structure for `friedman.test`
# Each column will be a model, and each row will be a dataset
friedman_result <- friedman.test(t(accuracy_data))
print(friedman_result)

# If significant, proceed with Dunn's test for pairwise comparisons
# install.packages("FSA")
library(FSA)

# Convert the data to long format for the test
accuracy_long <- stack(accuracy_data)
names(accuracy_long) <- c("Accuracy", "Model")

# Create a grouping factor for the datasets
accuracy_long$Dataset <- factor(rep(1:nrow(accuracy_data), times=ncol(accuracy_data)))

# Apply Dunn's test
dunn_result <- dunnTest(Accuracy ~ Model, data = accuracy_long, method = "bonferroni")
print(dunn_result)

```
###Sample Results Interpretation

Friedman Test Results:

Chi-Squared Value: 17.12 - This is the test statistic calculated by the Friedman test. It measures the overall difference in rankings of the models across datasets. A higher value suggests greater differences among the models.

Degrees of Freedom (df): 4 - The degrees of freedom are calculated as k - 1, where k is the number of models. Since there are 5 models (Logistic Regression, AdaBoost, SVM, Naive Bayes, GBM), the degrees of freedom are 5 - 1 = 4.

P-Value: 0.001832 - This is the probability that the observed differences could have happened by chance. Since the p-value is much less than 0.05, it indicates a statistically significant difference in performance among the models across the datasets.

The Friedman test shows that there is a significant difference between the models’ performances. Which indicates that at least one model performs differently.


Dunn's Test Results: 

Comparison: This column lists all pairwise comparisons between the models (e.g., AdaBoost vs. GBM, Logistic Regression vs. SVM Linear).

Z: The Z-score for each comparison, indicating the standardized difference between the models.

P.unadj: The unadjusted p-value, which reflects the raw significance level without any correction for multiple comparisons.

P.adj: The adjusted p-value, corrected using the Bonferroni method to control the risk of Type I errors (false positives) when performing multiple pairwise comparisons.


GBM - Naive_Bayes: The adjusted p-value (0.022) is less than 0.05, indicating a statistically significant difference between GBM and Naive Bayes. This suggests that GBM performs significantly differently (likely better or worse) compared to Naive Bayes across the datasets.