---
title: "DMLR DeFi Survival Data Pipeline Example"
author: "Hanzhen Qin(qinh2)"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  pdf_document: 
    latex_engine: xelatex
  html_document:
    toc: true
    number_sections: true
    df_print: paged
---

```{r, include=FALSE}
# Check and install required R packages
if (!require("conflicted")) {
  install.packages("conflicted", dependencies = TRUE)
  library(conflicted)
}

# Set default CRAN repository
local({
  r <- getOption("repos")
  r["CRAN"] <- "http://cran.r-project.org"
  options(repos = r)
})

# Define the list of required packages
required_packages <- c(
  "rmarkdown", "tidyverse", "stringr", "ggbiplot", "pheatmap", 
  "caret", "survival", "survminer", "ggplot2", 
  "kableExtra", "rpart", "glmnet", "data.table", "reshape2", 
  "pander", "readr", "dplyr", "e1071", "ROSE", "xgboost", "parallel"
)

# Loop through the package list and install missing packages
for (pkg in required_packages) {
  if (!require(pkg, character.only = TRUE)) {
    install.packages(pkg, dependencies = TRUE)
    library(pkg, character.only = TRUE)
  }
}

# Handle function name conflicts
conflict_prefer("slice", "dplyr")
conflict_prefer("filter", "dplyr")

# Set knitr options for R Markdown
knitr::opts_chunk$set(echo = TRUE)

# Rename dplyr functions to avoid conflicts with other packages
select <- dplyr::select
rename <- dplyr::rename
summarize <- dplyr::summarize
group_by <- dplyr::group_by
```

# Survival Data Pipeline

* Project name: DMLR DeFi-LTM

```{r}
source("~/DMLR_DeFi_Survival_Dataset_And_Benchmark/source/survivalData_pipeline/data_preprocessing.R")
source("~/DMLR_DeFi_Survival_Dataset_And_Benchmark/source/survivalData_pipeline/model_evaluation_visual.R")
source("~/DMLR_DeFi_Survival_Dataset_And_Benchmark/source/survivalData_pipeline/classification_models.R")
source("~/DMLR_DeFi_Survival_Dataset_And_Benchmark/source/survivalData_pipeline/get_classification_cutoff.R")
```

```{r}
# set the indexEvent and outcomeEvent
indexEvent = "borrow"
outcomeEvent = "deposit"

# load the corresponding train and test data
get_train_test_data(indexEvent, outcomeEvent)

# If you want to check the train and test data, you can run the following codes.
# cat("Train data:\n")
# summary(train)
# cat("Test data:\n")
# summary(test)
```

Using the `get_classification_cutoff` funtion to get the optimal timeDiff, then we will call the `data_processing` function above to get all the training data and test data.

```{r}
classification_cutoff = get_classification_cutoff(indexEvent, outcomeEvent)
train_data = data_processing(train, classification_cutoff)
test_data = data_processing(test, classification_cutoff)
```

```{r}
# If you want to watch the percentages between "Yes" and "No" label, run this code.
get_percentage(train_data, indexEvent, outcomeEvent)
```

If the ratio of "No" labels to "Yes" labels in the dataset is significantly imbalanced, we can utilize the `smote_data` function to generate a new, more balanced dataset. This balanced dataset ensures that both classes are better represented, helping to mitigate the bias introduced by class imbalance and ultimately improving the accuracy and reliability of our classification model.

```{r}
train_data <- smote_data(train_data)
```

Then you can check the updated balanced version of train data.

```{r}
# If you want to watch the percentages between "Yes" and "No" label, run this code.
get_percentage(train_data, indexEvent, outcomeEvent)
```

After obtaining the train and test data, we will apply all the classification models to evaluate the relationship between these events.

```{r}
lr_return = logistic_regression(train_data, test_data)
accuracy_lr_dataframe = lr_return$metrics_lr_dataframe
accuracy_lr = lr_return$metrics_lr
```

```{r}
dt_return = decision_tree(train_data, test_data)
accuracy_dt_dataframe = dt_return$metrics_dt_dataframe
accuracy_dt = dt_return$metrics_dt
```

```{r}
nb_return = Naive_bayes(train_data, test_data)
accuracy_nb_dataframe = nb_return$metrics_dataframe
accuracy_nb = nb_return$metrics
```

```{r}
xgb_return = XG_Boost(train_data, test_data)
accuracy_xgb_dataframe = xgb_return$metrics_xgb_dataframe
accuracy_xgb = xgb_return$metrics_xgb
```

```{r}
en_return = elastic_net(train_data, test_data)
accuracy_en_dataframe = en_return$metrics_en_dataframe
accuracy_en = en_return$metrics_en
```

```{r}
# compare all the classification models
metrics_list_BD <- list(
  list(accuracy_lr, "Logistic Regression"), 
  list(accuracy_dt, "Decision Tree"), 
  list(accuracy_nb, "Naive Bayes"), 
  list(accuracy_xgb, "XGBoost"), 
  list(accuracy_en, "Elastic Net")
)
accuracy_comparison_plot(metrics_list_BD)
```

```{r}
# Show the final dataframe for all classification models,
# including the classification model name, accuracy, data combination name.
data_name_BD <- paste(indexEvent, "+", outcomeEvent)
accuracy_dataframe_list_BD <- list(accuracy_lr_dataframe, accuracy_dt_dataframe, 
                                   accuracy_nb_dataframe, accuracy_xgb_dataframe, 
                                   accuracy_en_dataframe)
combined_results_BD <- combine_classification_results(accuracy_dataframe_list_BD, data_name_BD)

# display the combined dataframe
pander(combined_results_BD, caption = "Classification Model Performance")
```

```{r}
# set the indexEvent and outcomeEvent
indexEvent = "borrow"
outcomeEvent = "repay"

# load the corresponding train and test data
get_train_test_data(indexEvent, outcomeEvent)

classification_cutoff = get_classification_cutoff(indexEvent, outcomeEvent)
train_data = data_processing(train, classification_cutoff)
test_data = data_processing(test, classification_cutoff)
```

```{r}
# If you want to watch the percentages between "Yes" and "No" label, run this code.
get_percentage(train_data, indexEvent, outcomeEvent)
```

```{r}
lr_return = logistic_regression(train_data, test_data)
accuracy_lr_dataframe = lr_return$metrics_lr_dataframe
accuracy_lr = lr_return$metrics_lr
```

```{r}
dt_return = decision_tree(train_data, test_data)
accuracy_dt_dataframe = dt_return$metrics_dt_dataframe
accuracy_dt = dt_return$metrics_dt
```

```{r}
nb_return = Naive_bayes(train_data, test_data)
accuracy_nb_dataframe = nb_return$metrics_dataframe
accuracy_nb = nb_return$metrics
```

```{r}
xgb_return = XG_Boost(train_data, test_data)
accuracy_xgb_dataframe = xgb_return$metrics_xgb_dataframe
accuracy_xgb = xgb_return$metrics_xgb
```

```{r}
en_return = elastic_net(train_data, test_data)
accuracy_en_dataframe = en_return$metrics_en_dataframe
accuracy_en = en_return$metrics_en
```

```{r}
# compare all the classification models
metrics_list_BR <- list(
  list(accuracy_lr, "Logistic Regression"), 
  list(accuracy_dt, "Decision Tree"), 
  list(accuracy_nb, "Naive Bayes"), 
  list(accuracy_xgb, "XGBoost"), 
  list(accuracy_en, "Elastic Net")
)
accuracy_comparison_plot(metrics_list_BR)
```

```{r}
# Show the final dataframe for all classification models,
# including the classification model name, accuracy, data combination name.
data_name_BR <- paste(indexEvent, "+", outcomeEvent)
accuracy_dataframe_list_BR <- list(accuracy_lr_dataframe, accuracy_dt_dataframe, 
                                    accuracy_nb_dataframe, accuracy_xgb_dataframe, 
                                    accuracy_en_dataframe)
combined_results_BR <- combine_classification_results(accuracy_dataframe_list_BR, data_name_BR)

# display the combined dataframe
pander(combined_results_BR, caption = "Classification Model Performance")
```

```{r}
# set the indexEvent and outcomeEvent
indexEvent = "borrow"
outcomeEvent = "withdraw"

# load the corresponding train and test data
get_train_test_data(indexEvent, outcomeEvent)

classification_cutoff = get_classification_cutoff(indexEvent, outcomeEvent)
train_data = data_processing(train, classification_cutoff)
test_data = data_processing(test, classification_cutoff)
```

```{r}
# If you want to watch the percentages between "Yes" and "No" label, run this code.
get_percentage(train_data, indexEvent, outcomeEvent)
```

```{r}
train_data <- smote_data(train_data)
get_percentage(train_data, indexEvent, outcomeEvent)
```

```{r}
lr_return = logistic_regression(train_data, test_data)
accuracy_lr_dataframe = lr_return$metrics_lr_dataframe
accuracy_lr = lr_return$metrics_lr
```

```{r}
dt_return = decision_tree(train_data, test_data)
accuracy_dt_dataframe = dt_return$metrics_dt_dataframe
accuracy_dt = dt_return$metrics_dt
```

```{r}
nb_return = Naive_bayes(train_data, test_data)
accuracy_nb_dataframe = nb_return$metrics_dataframe
accuracy_nb = nb_return$metrics
```

```{r}
xgb_return = XG_Boost(train_data, test_data)
accuracy_xgb_dataframe = xgb_return$metrics_xgb_dataframe
accuracy_xgb = xgb_return$metrics_xgb
```

```{r}
en_return = elastic_net(train_data, test_data)
accuracy_en_dataframe = en_return$metrics_en_dataframe
accuracy_en = en_return$metrics_en
```

```{r}
# compare all the classification models
metrics_list_BW <- list(
  list(accuracy_lr, "Logistic Regression"), 
  list(accuracy_dt, "Decision Tree"), 
  list(accuracy_nb, "Naive Bayes"), 
  list(accuracy_xgb, "XGBoost"), 
  list(accuracy_en, "Elastic Net")
)
accuracy_comparison_plot(metrics_list_BW)
```

```{r}
# Show the final dataframe for all classification models,
# including the classification model name, accuracy, data combination name.
data_name_BW <- paste(indexEvent, "+", outcomeEvent)
accuracy_dataframe_list_BW <- list(accuracy_lr_dataframe, accuracy_dt_dataframe, 
                                   accuracy_nb_dataframe, accuracy_xgb_dataframe, 
                                   accuracy_en_dataframe)
combined_results_BW <- combine_classification_results(accuracy_dataframe_list_BW, data_name_BW)

# display the combined dataframe
pander(combined_results_BW, caption = "Classification Model Performance")
```

```{r}
# set the indexEvent and outcomeEvent
indexEvent = "borrow"
outcomeEvent = "account liquidated"

# load the corresponding train and test data
get_train_test_data(indexEvent, outcomeEvent)

classification_cutoff = get_classification_cutoff(indexEvent, outcomeEvent)
train_data = data_processing(train, classification_cutoff)
test_data = data_processing(test, classification_cutoff)
```

```{r}
# If you want to watch the percentages between "Yes" and "No" label, run this code.
get_percentage(train_data, indexEvent, outcomeEvent)
```

```{r}
train_data <- smote_data(train_data)
get_percentage(train_data, indexEvent, outcomeEvent)
```

```{r}
lr_return = logistic_regression(train_data, test_data)
accuracy_lr_dataframe = lr_return$metrics_lr_dataframe
accuracy_lr = lr_return$metrics_lr
```

```{r}
dt_return = decision_tree(train_data, test_data)
accuracy_dt_dataframe = dt_return$metrics_dt_dataframe
accuracy_dt = dt_return$metrics_dt
```

```{r}
nb_return = Naive_bayes(train_data, test_data)
accuracy_nb_dataframe = nb_return$metrics_dataframe
accuracy_nb = nb_return$metrics
```

```{r}
xgb_return = XG_Boost(train_data, test_data)
accuracy_xgb_dataframe = xgb_return$metrics_xgb_dataframe
accuracy_xgb = xgb_return$metrics_xgb
```

```{r}
en_return = elastic_net(train_data, test_data)
accuracy_en_dataframe = en_return$metrics_en_dataframe
accuracy_en = en_return$metrics_en
```

```{r}
# compare all the classification models
metrics_list_BAL <- list(
  list(accuracy_lr, "Logistic Regression"), 
  list(accuracy_dt, "Decision Tree"), 
  list(accuracy_nb, "Naive Bayes"), 
  list(accuracy_xgb, "XGBoost"), 
  list(accuracy_en, "Elastic Net")
)
accuracy_comparison_plot(metrics_list_BAL)
```

```{r}
# Show the final dataframe for all classification models,
# including the classification model name, accuracy, data combination name.
data_name_BAL <- paste(indexEvent, "+", outcomeEvent)
accuracy_dataframe_list_BAL <- list(accuracy_lr_dataframe, accuracy_dt_dataframe, 
                                   accuracy_nb_dataframe, accuracy_xgb_dataframe, 
                                   accuracy_en_dataframe)
combined_results_BAL <- combine_classification_results(accuracy_dataframe_list_BAL, data_name_BAL)

# display the combined dataframe
pander(combined_results_BAL, caption = "Classification Model Performance")
```

## Classification Model Performance For All Data Combinations

After we run all the data combinations, we can use the `combine_accuracy_dataframes` to combine all the classification models' performance into one dataframe.

```{r}
combined_classification_results <- combine_accuracy_dataframes(
  list(combined_results_BAL, combined_results_BD, combined_results_BR, combined_results_BW))
pander(combined_classification_results, caption = "Classification Model Performance for all data")
```

## Generating Dataframe For Specified Accuracy

This section is only for a special need, not required for the whole pipeline workflow!!!

In this section, the final output is a combined data frame that consolidates performance metrics for multiple classification models across different data scenarios. Each row represents a specific scenario (e.g., "borrow + withdraw" or "borrow + repay"), while the columns display the selected performance metric (e.g., "balanced_accuracy") and the corresponding values for each classification model (e.g., Logistic Regression, Decision Tree). 

```{r}
ba_accuracy_dataframe_BAL <- specific_accuracy_statistics(data_name_BAL, "balanced_accuracy", 
                                                      metrics_list_BAL)
ba_accuracy_dataframe_BD <- specific_accuracy_statistics(data_name_BD, "balanced_accuracy", 
                                                      metrics_list_BD)
ba_accuracy_dataframe_BR <- specific_accuracy_statistics(data_name_BR, "balanced_accuracy", 
                                                      metrics_list_BR)
ba_accuracy_dataframe_BW <- specific_accuracy_statistics(data_name_BW, "balanced_accuracy", 
                                                      metrics_list_BW)
combined_accuracy_dataframe <- combine_accuracy_dataframes(
  list(ba_accuracy_dataframe_BAL, ba_accuracy_dataframe_BD, ba_accuracy_dataframe_BR, 
       ba_accuracy_dataframe_BW))
pander(combined_accuracy_dataframe, caption = "Combined accuracy dataframe")
```